A hierarchical model to evaluate pest treatments from prevalence and intensity data

### 2023-02-02 Article.qmd
-

```{r inference_example_real_data, cache = FALSE, eval = TRUE, results = 'hide'}
# Jags code for the model  #################################################
modelstringYZ = "
    model {

@@

@@

# Building scenarios #######################################################
seed = 1;   I = 10
data = suppressMessages(simu_data(seed = seed, I = I))

>>>>

```{r inference_example_real_data, cache = FALSE, eval = TRUE, results = 'hide'}
# The following code presents the inference on an extract fo the real 
# dataset, which includes both trials of figure 1B (2020 - B1A97 ; 2020 - 
# u1CwE). It is  a demo for the "50% Y / 50% Z" scenario and we set here the 
# number of adaptation and iteration to 2000 in order to reduce computation 
# time.

# Jags code for the model  #################################################
modelstringYZ = "
    model {

@@

# Building scenarios -------------------------------------------------------
scenarioY = data %>% mutate(Z = NA)
scenarioYhalfZhalf = data %>% mutate(Y = ifelse(ID == "2020 - B1A97", Y, NA), 
                                     Z = ifelse(ID == "2020 - B1A97", NA, Z))
scenarioYhalf = data %>% filter(ID == "2020 - B1A97") %>% mutate(Z = NA)
scenarioZhalf = data %>% filter(ID == "2020 - u1CwE") %>% mutate(Y = NA)
# ---------------------------------------------------------------------------

data = scenarioYhalfZhalf

@@

# Building scenarios #######################################################
# Scenarios "50% Y" and "50% Z" are obtained from scenarios "100% Y" and 
# "100% Z", respectively. For example "50% Y" scenario with 40 trials 
# corresponds to "100% Y" with 20 trials.

seed = 1;   I = 10
data = suppressMessages(simu_data(seed = seed, I = I))
